Fish do not need visas: the transboundary nature of the world’s exploited marine fish species (79/96 characters)

### 2020-02-12 Initial_Analysis.Rmd
Did some updates

@@

# Read Sau Value Data (Thank you Tim!)
SAU_Revenue_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep ="")) %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise(mean_value = mean(value,na.rm=T)) %>% 
  left_join(Clean_sau_eez_fes)

@@

EEZ_Catch %>% 
  filter(
    reporting_status == "Reported",
    year > 2005) %>% 
  group_by(year) %>% 
  summarise(sum_year = sum(tonnes),
            sum_year_value = sum(landed_value)) %>% 
  group_by() %>% 
  summarise(mean(sum_year),
            mean(sum_year_value)
  )

Total_Catch_Spp <- 71842644/75202371

@@

Total_Trans_Rev <- SAU_Revenue_Data %>% 
  filter(taxon_key %in% Total_trans$taxon_key) %>% 
  group_by() %>% 
  summarise(Total =sum(mean_value)/1000000)# total revenue within EEZs of the world from sau.org

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high'))
  )

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  mutate(#fishing_entity = ifelse(fishing_entity == "USA","United States of America",
    # ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)
    # ),
    Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )
  ) %>% 
  filter(Total_USD > 0)

@@

### Revenue Data
Subregion_Data <- Revenue_Country %>% 
  left_join(Catch_Country,
            by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T)

@@

label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

@@

```{r Territory_Map_Round_Weighted, eval =F, echo =F}

>>>>

#### Determine Regions ezs areas

EEZ_Area <- World_sf %>% 
  as.data.frame() %>% 
  group_by(eez_name) %>% 
  summarise(Size_EEZ = sum(Area_km2))

Regional_Area <- World_sf %>% 
  as.data.frame() %>% 
  left_join(Clean_sau_eez_fes) %>% 
  left_join(UN_Regions) %>% 
  filter(fishing_entity %in% Clean_sau_eez_fes$fishing_entity) %>% 
  group_by(sub_region) %>% 
  summarise(Size_Region = sum(Area_km2))

@@

# Read Sau Value Data (Thank you Tim!)
SAU_Tim_Data <- fread(paste(Data_Path,"Distribution_Data/sau_catch_value_country_taxon_JEPA.csv", sep =""))

SAU_Sampled_Data <- Clean_sau_eez_fes %>%
  group_by(fishing_entity,fishing_entity_id) %>% 
  summarise(n=n()) %>% 
  left_join(SAU_Tim_Data, by = "fishing_entity_id") %>% 
  clean_names() %>% 
  group_by(fishing_entity_id,taxon_key) %>% 
  summarise_at(c("catch","value"),
               mean,na.rm=T) %>% 
  gather("Variable","Value",catch:value)

# Total sampled catch
Total_Catch <- SAU_Sampled_Data %>% 
  filter(Variable == "catch") %>% 
  group_by() %>% 
  summarize(sum(Value,na.rm=T)) %>% 
  pull()

@@

Total_Catch_Spp <- SAU_Sampled_Data/SAU_Total_EEZ_Data

@@

Total_Trans_Rev <- SAU_Sampled_Data %>% 
  semi_join(Tresholded_T_Data,
            by = c("taxon_key"))

  group_by() %>% 
  summarise(Total =sum(mean_value)/1000000)# total revenue within EEZs of the world from sau.org

@@

# Data per Territory
Transboundary_Spp <- Tresholded_T_Data %>% 
  group_by(eez_name) %>% 
  summarise(
    n_trans_spp = length(unique(taxon_key)),
    n_neighbours = length(unique(eez_neighbour)),
    trans_Rrate = n_trans_spp/n_neighbours
  ) %>% 
  left_join(EEZ_Area, 
            by = "eez_name") %>% 
  mutate(
    Bins = cut(n_trans_spp,breaks = 5),
    Bins_Plot = cut(n_trans_spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')),
    # Include the weighted method for supplementals
    Weight_Spp = ifelse(n_trans_spp/Size_EEZ < 1,1, n_trans_spp/Size_EEZ),
    Weight_Bins = cut(Weight_Spp,breaks = 5),
    Weight_Bins_Plot = cut(Weight_Spp,breaks = 5,
                    labels = c('super low', 'low','median', 'high','super high')
                    )
  )

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity","fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  ungroup() %>% 
  # left_join(EEZ_Area, 
            # by = "eez_name") %>% 
  mutate(
    Bins = cut(Total_USD,breaks = Rev_Breaks, dig.lab = 5 ),
    Bins_Plot = cut(Total_USD,breaks = Rev_Breaks,
                    labels = c('super low', 'low','median','high','super high'),
                    dig.lab = 5 # Removes scientific notaion
    )#,
     # Include the weighted method for supplementals
  #   Weight_Rev = Total_USD/Size_EEZ,
  #   Weight_Bins = cut(Weight_Rev,breaks = 5),
  #   Weight_Bins_Plot = cut(Weight_Rev,breaks = 5,
  #                   labels = c('super low', 'low','median', 'high','super high'))
  # )
  ) %>% 
  filter(Total_USD > 0)

@@

### Revenue Data
Subregion_Data <- Revenue_Country %>% 
  left_join(Catch_Country,
            by = "fishing_entity") %>% 
  left_join(UN_Regions,
            by = "fishing_entity") %>% 
  mutate(sub_region = ifelse(is.na(sub_region), "Other",paste(sub_region))) %>% 
  left_join(Regional_Area, 
            by = "sub_region") %>% 
  mutate(
    Weighted_Catch = fishing_entity_catch/Size_Region,
    Weighted_USD = Total_USD/Size_Region
    ) %>% 
  group_by(sub_region) %>% 
  summarise_if(is.numeric,c(sum = sum,
                            m = mean,
                            sd = sd),
               na.rm=T)

@@

# Label info Rev
label_data_rev <- Subregion_Data_Trans %>% 
  arrange(Total_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

# Label info Catch
label_data_catch <- Subregion_Data_Trans %>% 
  arrange(fishing_entity_catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

# Label info Weight Catch
label_data_w_catch <- Subregion_Data_Trans %>% 
  arrange(Weighted_Catch_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

# Label info Weight Catch
label_data_w_rev <- Subregion_Data_Trans %>% 
  arrange(Weighted_USD_sum) %>% # soo it looks like a nice snail :)
  mutate(
    id = seq(1,nrow(Subregion_Data_Trans)),
    angle = 90 -360 * (id-0.5)/number_of_bar,
    hjust = ifelse(angle < -90,1,0),
    angleb = ifelse(angle < -90, (angle +180), angle)
  ) %>% 
  mutate(
    sub_region = ifelse(str_detect(sub_region,"Latin"),"Ltn. Ame. &\nthe Car.",
                        ifelse(sub_region =="Northern America","Northern\nAmerica",
                               paste(sub_region))
    ),
    sub_region_n = paste(sub_region," (n=",n_trans_spp,")",sep = "")
  )

@@

```{r Weight_Revenue, eval =F, echo =F}

# Set plot limits
max_lim <- max(Subregion_Data_Trans$Weighted_USD_sum) +0.01

Rev_Plot <- ggplot(
  # Regional plots
  data = Subregion_Data_Trans, 
  aes(
    x=reorder(id,Weighted_USD_sum),
    y=Weighted_USD_sum, 
    fill=Weighted_USD_sum
  )
) +    
  ylim(-0.001, max_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Data_Trans,
             aes(
               x=reorder(id,Weighted_USD_m),
               y=Weighted_USD_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sds
  geom_errorbar(
    aes(
      ymin=ifelse(Weighted_USD_m-Weighted_USD_sd <= 0,0,Weighted_USD_m-Weighted_USD_sd), # sets lower to 0
      ymax=Weighted_USD_m+Weighted_USD_sd
    ),
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  # Looking good
  theme_minimal() +
  theme(
    legend.position = c(0.73,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-10,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 1, y = 1, xend = 17, yend = 17),  
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_w_rev, 
            aes(x=id,
                y=Weighted_USD_sum+0.0001,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_rev$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       colours = pal#,
                       # limits = c(0,16500),
                       # breaks = seq(0,16000,4000)
                       ) +
  guides(fill = guide_colorbar(label.position = "left")
  )

###____________###
### Catch plot
###____________###
max_lim <- max(Subregion_Data_Trans$Weighted_Catch_sum) +0.001

Catch_Plot <- ggplot(data = Subregion_Data_Trans, 
                     aes(x=reorder(id,Weighted_Catch_sum),
                         y=Weighted_Catch_sum, 
                         fill=Weighted_Catch_sum
                     )
) +    
  ylim(-0.0003, max_lim) +
  geom_bar(stat="identity") +
  # Regional averages
  geom_point(data = Subregion_Data_Trans,
             aes(
               x=reorder(id,Weighted_Catch_sum),
               y=Weighted_Catch_m
             ),
             colour = "black",
             alpha = 0.5
  ) +
  # Regional sd's
  geom_errorbar(
    aes(
      ymin=ifelse(Weighted_Catch_m-Weighted_Catch_sd <= 0,0,Weighted_Catch_m-Weighted_Catch_sd),
      ymax=Weighted_Catch_m+Weighted_Catch_sd
    ), 
    width=.2,
    position=position_dodge(.9),
    alpha = 0.5) +
  theme_minimal() +
  theme(
    legend.position = c(0.1,0.60),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = margin(0,-10,-6,-5,"cm")
  )  +
  # Base line
  # geom_segment(aes(x = 0, y = 1, xend = 17, yend = 17),
  #              colour = "black", size=0.1, inherit.aes = FALSE) +
  coord_polar(start = 0) + 
  geom_text(data=label_data_w_catch, 
            aes(x=id,
                y=Weighted_Catch_sum+0.0001,
                label=sub_region,
                hjust=hjust), 
            color="black",
            fontface="bold",
            size=2, 
            angle= label_data_catch$angleb, 
            inherit.aes = FALSE) +
  scale_fill_gradientn("",
                       # limits = c(0,16.5),
                       # breaks = seq(0,16,4),
                       colours = pal

  );Catch_Plot

plot <- ggdraw() +
  # map
  # draw_plot(Map, x = 0, y = 0.45, width = 1, height = 0.58) +
  # Revenue circular
  draw_plot(Rev_Plot, x = 0.2, y = 0.5, width = 0.5, height = 0.4) +
  # Catch circular
  draw_plot(Catch_Plot, x = 0.46, y = 0.5, width = 0.5, height = 0.4) +
  # Labeks
  draw_plot_label(label = c("A", "B"), 
                  size = 20,
                  x = c(0.1, 0.5), 
                  y = c(1,1)
  ) +
  draw_plot_label(label = c("Revenue (USD) | Catch (Tones)","(Million)"), 
                  size = 8,
                  x = c(0.330,0.485), 
                  y = c(0.31,0.29)
  )

### 2020-02-12 Manuscript_Draft.Rmd
Did some updates

We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reported to FAO, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary. First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g. we did not include the high seas). Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods). The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data. A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive. Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.

>>>>

We overlaid the known distribution of 968 commercially valuable marine species responsable for **95%** of global EEZ catch reconstruced by the *Sea Around Us*, and the EEZ of 153 coastal countries, and developed a four-criteria methodology to determine if a species was transboundary. First we only considered shared species between neighboring EEZs, rather than the species' extended distribution (e.g. we did not include the high seas). Secondly, we considered a species to be present in a grid cell if all data sources predicted positive occurrence (see Methods). The third criteria determined whether a species was exploited within a given grid cell using spatially explicit catch data. A species was considered as present in a grid cell if both predicted species occurrences and catch data were positive. Finally, we determined a spatial threshold based on the proportion of the species' distribution within each neighboring EEZs to confirm occurance in both EEZs.
